Next Trippy Structures\thanks{Supported by organization x.}

### 2019-02-22 paper.tex
Explaining dataset

\begin{threeparttable}
\centering
\caption{Efficiency of \acumm~and \ctr~against the queries described in Section~\ref{sec:rq}}
\label{tab:queries}
\begin{tabular}{|l|l|l|}
\hline
Query &  \acumm & \ctr\\
\hline
\texttt{board\_X$_{LT}$} & $O(l)$\tnote{a} & \ctrq\tnote{b} \\
\texttt{alight\_X$_{LT}$} & $O(l)$\tnote{a} & Hard\tnote{cd} \\
\texttt{start\_X$_{LT}$} & - & \ctrq\tnote{b} \\
\texttt{end\_X$_{LT}$} & - & \ctrq\tnote{b} \\
\texttt{switch\_X$_{LT}$} & - & \ctrq\tnote{b} \\
\texttt{from\_X$_{LT}$\_to\_Y$_{LT}$} & - & \ctrq\tnote{b} \\
\texttt{board\_L$_T$} & O(1) & $O(|S| \times \ctrq)$\tnote{be} \\
\texttt{alight\_L$_T$} & O(1) & $O(|S| \times \ctrq)$\tnote{bce} \\
\texttt{start\_L$_T$} & - & $O(log(|L|\times\bar{|J^l|}))$\tnote{fg} \\
\texttt{end\_L$_T$} & - & $O(|S| \times \ctrq)$\tnote{be} \\
\texttt{board\_T} & $O(|L|)$\tnote{f} & Hard\tnote{d} \\
\texttt{alight\_T} & $O(|L|)$\tnote{f} & Hard\tnote{cd} \\
\texttt{start\_T} & - & $O(|L| \times log(|L|\times\bar{|J^l|}))$\tnote{fg} \\
\texttt{end\_T} & - & Hard\tnote{d} \\
\texttt{load\_X$_{LT}$} & $O(l)$\tnote{a} & Hard\tnote{cd} \\
\hline
\end{tabular}

@@

\section{Experiments}
\label{sec:exp}
In this section we discuss the practical performance of our structures. To evaluate them, we have run randomly generated queries against \acumm, \ttctr~and \ctr, with multiple configurations (TODO: describe configurations).

\subsection{Experimental dataset}
Write about the generation of Madrid dataset from real bus journeys.

@@

\begin{table}
    \caption{Space requirements for the CSA (a) and the WM (b) from \ttctr}
    \begin{subtable}[t]{.48\linewidth}
    \vspace{-12pt}
    \caption{\footnotesize (a)}
    \vspace{-12pt}
    \begin{tabular}[t]{|l|l|r|r|}
        \hline
        Param. & bps & Size (MiB) & Comp. (\%) \\
         \hline
        baseline & 16 & 67.85 & 100.00 \\
        32 & 7.288 & 30.91 & 45.55 \\
        128 & 6.069 & 25.74 & 37.93 \\
        512 & 5.761 & 24.43 & 36.01 \\
        \hline
    \end{tabular}
    \end{subtable}%
    \begin{subtable}[t]{.48\linewidth}
    \vspace{-12pt}
    \caption{\footnotesize (b)}
    \vspace{-12pt}
    \begin{tabular}[t]{|l|l|r|r|}
        \hline
        Param. & bps & Size (MiB) & Comp. (\%) \\
         \hline
        baseline & 14 & 42.68 & 100.00 \\
        RG32 & 14.438 & 44.02 & 103.13 \\
        RG32 & 13.478 & 41.09 & 96.27 \\
        RG64 & 12.79 & 38.99 & 91.36 \\
        RG128 & 12.446 & 37.94 & 88.90 \\
        \hline
    \end{tabular}
    \end{subtable}
\end{table}

\begin{table}
    \caption{Space requirements for the CSA (a), the WMJ (b) and the WML (c) from \ctr}
    \begin{subtable}[t]{.48\linewidth}
    \vspace{-12pt}
    \caption{\footnotesize (a)}
    \vspace{-12pt}
    \begin{tabular}[t]{|l|l|r|r|}
        \hline
        Param. & bps & Size (MiB) & Comp. (\%) \\
         \hline
        baseline & 14 & 59.37 & 100.00 \\
        32 & 6.956 & 29.50 & 49.69 \\
        128 & 5.727 & 24.29 & 40.91 \\
        512 & 5.417 & 22.97 & 38.69 \\
        \hline
    \end{tabular}
    \end{subtable}
    \begin{subtable}[t]{.48\linewidth}
    \vspace{-12pt}
    \caption{\footnotesize (b)}
    \vspace{-12pt}
    \begin{tabular}[t]{|l|l|r|r|}
        \hline
        Param. & bps & Size (MiB) & Comp. (\%) \\
         \hline
        baseline & 14 & 59.37 & 100.00 \\
        RG32 & 14.438 & 61.23 & 103.13 \\
        RG32 & 13.419 & 56.91 & 95.85 \\
        RG64 & 12.732 & 53.99 & 90.94 \\
        RG128 & 12.388 & 52.53 & 88.49 \\
        \hline
    \end{tabular}
    \end{subtable}
    \begin{subtable}[t]{.48\linewidth}
    \vspace{-12pt}
    \caption{\footnotesize (c)}
    \vspace{-12pt}
    \begin{tabular}[t]{|l|l|r|r|}
        \hline
        Param. & bps & Size (MiB) & Comp. (\%) \\
         \hline
        baseline & 14 & 59.37 & 100.00 \\
        RG32 & 14.438 & 61.23 & 103.13 \\
        RG32 & 13.419 & 56.91 & 95.85 \\
        RG64 & 12.732 & 53.99 & 90.94 \\
        RG128 & 12.388 & 52.53 & 88.49 \\
        \hline
    \end{tabular}
    \end{subtable}%
\end{table}

>>>>

\begin{threeparttable}
\centering
\caption{Efficiency of \acumm~and \ctr~against the queries described in Section~\ref{sec:rq}}
\label{tab:queries}
\begin{tabular}{|l|l|l|}
\hline
Query &  \acumm & \ctr\\
\hline
\texttt{board\_X$_{LT}$} & $O(l)$\tnote{a} & \ctrq\tnote{b} \\
\texttt{alight\_X$_{LT}$} & $O(l)$\tnote{a} & Hard\tnote{cd} \\
\texttt{start\_X$_{LT}$} & - & \ctrq\tnote{b} \\
\texttt{end\_X$_{LT}$} & - & \ctrq\tnote{b} \\
\texttt{switch\_X$_{LT}$} & - & \ctrq\tnote{b} \\
\texttt{from\_X$_{LT}$\_to\_Y$_{LT}$} & - & \ctrq\tnote{b} \\
\texttt{board\_L$_T$} & O(1) & $O(|S| \times \ctrq)$\tnote{be} \\
\texttt{alight\_L$_T$} & O(1) & $O(|S| \times \ctrq)$\tnote{bce} \\
\texttt{start\_L$_T$} & - & $O(log(|L|\times\bar{|J^l|}))$\tnote{fg} \\
\texttt{end\_L$_T$} & - & $O(|S| \times \ctrq)$\tnote{be} \\
\texttt{board\_T} & $O(|L|)$\tnote{f} & Hard\tnote{d} \\
\texttt{alight\_T} & $O(|L|)$\tnote{f} & Hard\tnote{cd} \\
\texttt{start\_T} & - & $O(|L| \times log(|L|\times\bar{|J^l|}))$\tnote{fg}~~ \\
\texttt{end\_T} & - & Hard\tnote{d} \\
\texttt{load\_X$_{LT}$} & $O(l)$\tnote{a} & Hard\tnote{cd} \\
\hline
\end{tabular}

@@

\section{Experiments}
\label{sec:exp}
In this section we discuss the practical performance of our structures. To evaluate them, we have run randomly generated queries against \acumm, \ttctr~and \ctr, with several configurations to study the trade-off between compression and query efficiency. For the \texttt{CSA} structures from \ttctr~and \ctr, we experiment with the $t_\Psi$ (sampling interval) factors of 32, 128 and 512. For the \texttt{WM} present in \ttctr, as well as in the two \texttt{WM} from \ctr, we analyze the compression achieved with the RRR bitvector described in \cite{Raman:2002:SID:545381.545411}, using block sizes of 32, 64 and 128, and compare it against a plain bitvector with a rank structure. \marginpar{\tiny Do we have any similar trade-off for \acumm?}

\subsection{Experimental dataset}
Using real GTFS descriptions of bus routes and schedules, we generated a synthetic dataset of user trips that aims to realistically imitate real user behaviour over a month. In this work, we combined the GTFS obtained for the networks of urban\footnote{\url{http://www.emtmadrid.es}} and interurban\footnote{\url{http://www.crtm.es}} buses for the city of Madrid. My head hurts right now, but the steps to generate user trips are:

\begin{enumerate}
    \item Extract stops an lines. A reversed direction makes a new line.
    \item Connect stops that are on walking distance (100 meters) from each other, or appear sequentially on the same line.
    \item Parse the schedules for bus trips.
    \item Generate a month of journeys from the schedules. This is used both to generate user trips and to build our common structures.
    \item Generate user trips starting from a random stop and with a binomial distribution for switching lines, where the user is allowed to wait up to 30 minutes.
    \item Profit.
\end{enumerate}

@@

\begin{table}
    \caption{Space requirements for the CSA (a) and the WM (b) from \ttctr}
    \begin{subtable}[t]{.48\linewidth}
    \vspace{-12pt}
    \caption{\footnotesize (a)}
    \vspace{-12pt}
    \begin{tabular}[t]{|l|l|r|r|}
        \hline
        Param. & bps & Size (MiB) & Comp. (\%) \\
         \hline
        baseline & 16 & 67.85 & 100.00 \\
        32 & 7.288 & 30.91 & 45.55 \\
        128 & 6.069 & 25.74 & 37.93 \\
        512 & 5.761 & 24.43 & 36.01 \\
        \hline
    \end{tabular}
    \end{subtable}%
    \begin{subtable}[t]{.48\linewidth}
    \vspace{-12pt}
    \caption{\footnotesize (b)}
    \vspace{-12pt}
    \begin{tabular}[t]{|l|l|r|r|}
        \hline
        Param. & bps & Size (MiB) & Comp. (\%) \\
         \hline
        baseline & 14 & 42.68 & 100.00 \\
        RG32 & 14.438 & 44.02 & 103.13 \\
        RRR32 & 13.478 & 41.09 & 96.27 \\
        RRR64 & 12.79 & 38.99 & 91.36 \\
        RRR128 & 12.446 & 37.94 & 88.90 \\
        \hline
    \end{tabular}
    \end{subtable}
\end{table}

\begin{table}
    \caption{Space requirements for the CSA (a), the WMJ (b) and the WML (c) from \ctr}
    \begin{subtable}[t]{.48\linewidth}
    \vspace{-12pt}
    \caption{\footnotesize (a)}
    \vspace{-12pt}
    \begin{tabular}[t]{|l|l|r|r|}
        \hline
        Param. & bps & Size (MiB) & Comp. (\%) \\
         \hline
        baseline & 14 & 59.37 & 100.00 \\
        32 & 6.956 & 29.50 & 49.69 \\
        128 & 5.727 & 24.29 & 40.91 \\
        512 & 5.417 & 22.97 & 38.69 \\
        \hline
    \end{tabular}
    \end{subtable}
    \begin{subtable}[t]{.48\linewidth}
    \vspace{-12pt}
    \caption{\footnotesize (b)}
    \vspace{-12pt}
    \begin{tabular}[t]{|l|l|r|r|}
        \hline
        Param. & bps & Size (MiB) & Comp. (\%) \\
         \hline
        baseline & 14 & 59.37 & 100.00 \\
        RG32 & 14.438 & 61.23 & 103.13 \\
        RRR32 & 13.419 & 56.91 & 95.85 \\
        RRR64 & 12.732 & 53.99 & 90.94 \\
        RRR128 & 12.388 & 52.53 & 88.49 \\
        \hline
    \end{tabular}
    \end{subtable}
    \begin{subtable}[t]{.48\linewidth}
    \vspace{-12pt}
    \caption{\footnotesize (c)}
    \vspace{-12pt}
    \begin{tabular}[t]{|l|l|r|r|}
        \hline
        Param. & bps & Size (MiB) & Comp. (\%) \\
         \hline
        baseline & 14 & 59.37 & 100.00 \\
        RG32 & 14.438 & 61.23 & 103.13 \\
        RRR32 & 13.419 & 56.91 & 95.85 \\
        RRR64 & 12.732 & 53.99 & 90.94 \\
        RRR128 & 12.388 & 52.53 & 88.49 \\
        \hline
    \end{tabular}
    \end{subtable}%
\end{table}
